---
title: "Exercise: Data Wrangling and Tidy Data"
author: "Author Name"
date: "`r Sys.Date()`"
output: openintro::lab_report
---

```{r load-packages, message=FALSE}
library(tidyverse)
library(openintro)
trial <- read_csv("trial.csv")
scores <- read_csv("scores.csv")
exercise3 <- read_csv("exercise3.csv")
```

### Exercise 1

```{r }
#trial

trial %>%
  pivot_wider(names_from = Treatment, values_from = Result) %>%
  mutate(Diff = Control - Treat)
```

### Exercise 2

```{r }
#scores

scores %>%
  pivot_longer(cols = c(Winter, Spring, Fall), names_to = "Quarter", values_to = "Total") %>%
  pivot_wider(names_from = Test, values_from = Total) %>%
  mutate(Total = Math + Writing)

```

### Exercise 3
pivot long
unite
pivot wider

```{r }
exercise3

exA <- exercise3 %>%
  pivot_longer(cols = c(meanL, sdL, meanR, sdR), names_to = "type", values_to = "value") %>%
  unite(sex.type, sex, type, sep = ".") %>%
  pivot_wider(names_from = sex.type, values_from = value)
  
  #unite and pivot wider in 1 step
  #pivot_wider(names_from = c(sex, type), values_from = value, names_sep = ".")

exA 
```

```{r }
exB <- exA %>%
  pivot_longer(cols = c(F.meanL,F.sdL,F.meanR,F.sdR,M.meanL,M.sdL,M.meanR,M.sdR)) %>%
  separate(col = name, into = c('sex','type'), sep='\\.') %>%
  pivot_wider(names_from = type, values_from = value)

exB
```

### Exercise 4

a) Exercise 1 is preferable because it shows the control conditions value. It is easier to see the difference.
```{r }
ds1 <- data.frame(ID=c(1,2,3,1,2,3),
                  Treatment=c("T","T","T","C","C","C"),
                  Result=c(11,15,17,13,10,13))

Treat <- filter(ds1, Treatment == "T")
Control <- filter(ds1, Treatment == "C")
all <- mutate(Treat, Diff = Treat$Result - Control$Result)
all
```
b) It is possible that this method will wrongly matched the data to compute if the data isn't sorted correctly.

```{r }

ds2 <- data.frame(ID=c(2,1,3,1,2,3),
                  Treatment=c("T","T","T","C","C","C"),
                  Result=c(15,11,17,13,10,13))

Treat <- filter(ds2, Treatment == "T")
Control <- filter(ds2, Treatment == "C")
all2 <- mutate(Treat, Diff = Treat$Result - Control$Result)
all2
```
c) The program would crash since there aren't enough data for it to compute. This method requires all value to exist.

```{r eval=F}
ds3 <- data.frame(ID=c(1,2,3,1,2,3),
                  Treatment=c("T","C"),
                  Result=c(11,15,17,13,10,13))

Treat <- filter(ds3, Treatment == "T")
Control <- filter(ds3, Treatment == "C")
all3 <- mutate(Treat, Diff = Treat$Result - Control$Result)
all3
```
