---
title: "Data Wrangling Exercises"
author: "Sanyapoom Sirijirakarn"
date: "`r Sys.Date()`"
output: openintro::lab_report
---

```{r load-packages, message=FALSE}
library(tidyverse)
library(openintro)
library(mdsr)
library(babynames)
BabyNames <- make_babynames_dist()
```

### Exercise 1


```{r}
filterName <- function(x){
  varName <- deparse(substitute(x))
  
  BabyNames %>%
  filter(name == varName) %>%
  group_by(year) %>%
  summarize(total_n = sum(n)) %>%
  arrange(desc(total_n)) %>%
  head(5)
}

filterName(Sam)

```

### Exercise 2

A)
  1) Get the data Babynames
  2) Filter to baby names from 1990, can also filter male and female, can also use group by to leave out information we do not need
  3) Arrange it from the most name used to the lowest
  4) Show the first 10 names which would be most commonly used baby names from 1990
  
B) between() function returns a boolean value True or False. It checks whether the given value is in between the given range. I do not think you can use it for the previous exercise as between can only be use for numeric value. It is unable to evaluate strings.

```{r}
#For both male and female with only information we need
BabyNames %>%
  filter(between(year, 1990, 1999)) %>%
  group_by(name, sex) %>%
  summarize(total_n = sum(n)) %>%
  arrange(desc(total_n)) %>%
  head(10)

#For male baby names
BabyNames %>%
  filter(between(year, 1990, 1999), sex == "M") %>%
  group_by(name, sex) %>%
  summarize(total_n = sum(n)) %>%
  arrange(desc(total_n)) %>%
  head(10)

#For female baby names
BabyNames %>%
  filter(between(year, 1990, 1999), sex == "F") %>%
  group_by(name, sex) %>%
  summarize(total_n = sum(n)) %>%
  arrange(desc(total_n)) %>%
  head(10)


#For both male and female, original
BabyNames %>%
  filter(between(year, 1990, 1999)) %>%
  arrange(desc(n)) %>%
  head(10)

```
