---
title: "Jan 19"
author: "Sanyapoom Sirijirakarn"
date: "`r Sys.Date()`"
output: openintro::lab_report
---

```{r load-packages, message=FALSE}
library(tidyverse)
library(openintro)
data(mpg)
library(mosaic)
data(Galton)
```

### Exercise 1

Overplotting of points. You can improve it by adding jitter to see the overall trend of the graph better.

```{r }
ggplot(data = mpg, mapping = aes(x = cty, y = hwy)) + 
  geom_point()

ggplot(data = mpg, mapping = aes(x = cty, y = hwy)) + 
  geom_point(position = "jitter")
```

### Exercise 2

Width and height control the amount of jittering.

```{r }

```

### Exercise 4

coord_fixed() is important because it will configured the graph to a 1:1 ratio for x and y which will make it easier for us to analyze the data. geom_abline() only adds a reference line into the graph.

As city mpg grows, so does hwy mpg grows.

```{r }
ggplot(data = mpg, mapping = aes(x = cty, y = hwy)) +
  geom_point() + 
  geom_abline() +
  coord_fixed()

ggplot(data = mpg, mapping = aes(x = cty, y = hwy)) +
  geom_point() + 
  geom_abline()
```

### Exercise 5



```{r }
ggplot(data = Galton, aes(x = height, y = father)) +
  geom_point() +
  facet_grid(. ~ sex) +
  geom_smooth(method='lm')

ggplot(data = Galton, aes(x = height, y = father)) +
  geom_point() +
  facet_grid(sex ~ .) +
  geom_smooth(method='lm')
```

### Exercise 6



```{r }
library(mosaicData)
data(Marriage)

ggplot(data = Marriage, aes(x = ceremonydate   , y = officialTitle , color = race, group = person, size = age)) +
  geom_point(alpha = 0.6)  +
  facet_grid(. ~ person)



```

```{r }
library(mosaicData)
data(Marriage)

ggplot(data = Marriage, aes(x = prevcount    , y =   appdate   , color = prevconc, size = age)) +
  geom_point(alpha = 0.6)  +
  facet_grid(. ~ person)



```

